SPARQL on the Open, Decentralised Web

### 2016-11-15 dissertation/introduction.tex
Create problem overview #27 Map papers to problems #31 Reference papers from contrib #26

@@

The present work is located at the confluence of several contemporary
efforts in the Semantic Web community. The focus is on query answering
with the SPARQL query language, with emphasis on exploiting the World
Wide Web, but it touches upon query federation, hypermedia, empiricial
methods for evaluating performance, standards compliance and even
philosophy of science.

@@

\subsection{Design of Experiments}

@@

\subsection{Development problems}

@@

\subsection{Survey of HTTP Caching}

@@

\subsection{Philosophy of Science}

@@

\begin{enumerate}
\item 5 Free Software packages that have been accepted into the recent
  versions of the Debian GNU/Linux operating system.
\item Further 5 packages that already were accepted in Debian have been
  enhanced in the course of this work.
\item Contributions to the code base were accepted by another 5
  external projects.
\end{enumerate}

>>>>

\section{Research Problems Overview}\label{sec:problemsum}

The present work is located at the confluence of several contemporary
efforts in the Semantic Web community. The focus is on query answering
with the SPARQL query language, with emphasis on exploiting the World
Wide Web, but it touches upon query federation, hypermedia, empiricial
methods for evaluating performance, standards compliance and even
philosophy of science. A comprehensive treatment of research problems
are given in Section~\ref{sec:problems}, but to understand the
following contributions, the overarching problems are as follows:

It is difficult to many developers to interact with RDF, and
contributions to alleviate that are summarised in
Section~\ref{sec:schm}.

We have found that in few cases, at least when evaluating SPARQL
Engines, the evaluation has had a basis in sound statistics or in
philosophy of science and therefore the validity of the conclusions
drawn from them should be challenged. We contributed a new direction
to the statistical problem in Section~\ref{sec:scdoe} and a
philosophical discussion in Section~\ref{sec:scphil}.

To create a framework that allows the flexible and at the same time
efficient manner is difficult. Conventionally, the query engine would
break down a query to individual triple pattern matches, which did not
allow for much optimisation, or to easily modify the query
planning. Our contributions towards these problems are summarised in
Section~\ref{sec:scdev}.

As noted, the HTTP standard and the Web architecture allows for
caching responses, and in Section~\ref{sec:scsurvey} we detail
contributions to understand the contemporary usage of these
mechanisms. This is particularly interesting in the context of SPARQL
query execution on the Web, as currently, the infrastructure cannot
support evaluating arbitrary queries across the Web in a reliable
manner. A situation where the client, a caching proxy and a server may
share the work when evaluating a query results in a number of research
problems that are detailed in Section~\ref{sec:perfproblems}, and we
attempted to contribute an approach to some of these problems in
Chapter~\ref{sec:tpfcacheplanning} without reaching any solid
conclusions.

@@

In this section, we summarise the contributions of this work, with
reference to the detailed problem descriptions in
Section~\ref{sec:problems}, as well as
Section~\ref{sec:papersincontext}, where the papers are described and
put in context.

\subsection{Hypermedia}\label{sec:schm}

The following contributions were made towards Problem~\ref{prob:lapis}
in the paper described in Section~\ref{sec:conlapis}:

@@

\subsection{Design of Experiments}\label{sec:scdoe}

The following contributions were made towards Problem~\ref{prob:badstats}
in the paper described in Section~\ref{sec:condoe}:

@@

\subsection{Development problems}\label{sec:scdev}

The following contributions were made towards
problems~\ref{prob:breakdown},~\ref{prob:complexapi}~and~\ref{prob:dontjustpass}
in the paper described in Section~\ref{sec:conpush}:

@@

\subsection{Survey of HTTP Caching}\label{sec:scsurvey}

The following contribution was made towards Problem~\ref{prob:sanity}
in the papers described in Section~\ref{sec:consanity}:

@@

\subsection{Philosophy of Science}\label{sec:scphil}

The following contribution was made towards Problem~\ref{prob:badphil}
in the paper described in Section~\ref{sec:conphil}:

@@

In addition to papers, the following contributions were made in terms
of Free Software:

\begin{enumerate}
\item 5 packages that have been accepted into the recent
  versions of the Debian GNU/Linux operating system.
\item Further 5 packages that already were accepted in Debian have been
  enhanced in the course of this work.
\item Contributions to the code base were accepted by another 5
  external projects.
\end{enumerate}
